---
title: "Lab 3"
format: html
---

```{r setup}
#| setup: false
```

# Model background

# Exercise 1

```{r}
source(here::here("MCMC-2", "03-SIR2", "coding.R"))
source(here::here("MCMC-2", "03-SIR2", "mcmc-Markov.R"))
print(mcmcSIR.Markov)
```

# Exercise 2

Reading the data.

```{r}
dat <- read.table(here::here("MCMC-2", "03-SIR2", "data.txt"), header=TRUE)
```

```{r}
head(dat)
```

# Exercise 3

We want to fit a non-Markov SIR model where we assume that
$$R_i - I_i \sim \mathrm{Gamma}(\alpha, \gamma).$$
Then, 
$$E[R_i - I_i] = \alpha / \gamma.$$
The parameter $\alpha$ is treated as fixed and known, but we assume that $\beta$ and $\gamma$ are random, as described above.

Then, the unnormalized posterior density of interest is
$$\pi(\beta, \gamma, \mathbf{I} \mid \mathbf{R}) \propto \pi(\mathbf{I}, \mathbf{R} \mid \beta, \gamma) \pi(\beta)\pi(\gamma),$$
which is
$$whatever.$$

Then, the full conditional distributions are 
$$\pi(\beta \mid \gamma, \mathbf{I}, \mathbf{R}) = something;$$
$$\pi(\gamma \mid \beta, \mathbf{R}, \mathbf{R}) = something;$$
and
$$\pi(\mathbf{I}\mid \gamma, \beta, \mathbf{R}) = something.$$

# Exercise 4

We will write a function in R that will draw samples from $\pi(\beta, \gamma, \mathbf{I} \mid \mathbf{R})$ using MCMC.

```{r}
mcmcSIR_gamma <- function() {
	
}
```


